 Casting multiple shadows: interactive data visualisation with tours and embeddings

### 2020-01-30 paper.Rmd
move paper to top level

---
title: " Casting multiple shadows: interactive data visualisation with tours and embeddings"
description: |
  A new article created using the Distill format.
author:
  - name: Stuart Lee
    affiliation: Monash University
  - name: Di Cook
    affiliation: Monash University
date: "`r Sys.Date()`"
output: distill::distill_article
---

>>>>

---
title: " Casting multiple shadows: interactive data visualisation with tours and embeddings"
author:
  - name: Stuart Lee
    affiliation: Monash University
  - name: Di Cook
    affiliation: Monash University
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: liminal.bib
---
